LAGOS lake depth

### 2019-10-09 lagos_depth.Rmd
typo fix

# gg_raster <- cowplot::plot_grid( 
gg_convave_raster <- ggplot(data = as.data.frame(rsub1, xy = TRUE)) +
  geom_raster(aes(x = x, y = y, fill = layer)) +
  coord_quickmap() +
  scale_fill_continuous(tran = "reverse") +
  labs(fill = "") + ggtitle("concave") +
  theme_void()

>>>>

# gg_raster <- cowplot::plot_grid( 
gg_concave_raster <- ggplot(data = as.data.frame(rsub1, xy = TRUE)) +
  geom_raster(aes(x = x, y = y, fill = layer)) +
  coord_quickmap() +
  scale_fill_continuous(tran = "reverse") +
  labs(fill = "") + ggtitle("concave") +
  theme_void()
